Digital Authoritarianism and Western Foreign Aid

### 2022-09-22 Plan.tex
hypotheses

>>>>

We need to be more innocent about this project. We really don't know what is going on. There seem to be some alternative hypotheses: internet infrastructure good for recipient country and donors altruistic, recipients declare that is a need and donors responsive whether self-interested or not. Our hypothesis: donor countries interested in internet infrastructure to prevent China from blocking/subverting West's digital access in these countries...
